### 2022-12-06 chapters/literature/draft_citations.tex
update : university logo

% depends on the scientific usage there are two apporaches :
% 1. extern one or independent : when the most of researchs are using
% the benifits of this is the simplicity of instalation however we pay the price either with a lack of temporal resolution ( low frequency ) or the spatial granularity
% ( most of them measure the energy consumption of the whole machine )
% 2. dedicated one , they are based on the instrumentation of some parts of the computer , however they have a high cost and they are defficult to scale since they require an instrumentation of the execusion environment.
According to \citeauthor{hackenberg2014hdeem}, there are four main criteria to evaluate an energy measurement tool~\cite{hackenberg2014hdeem}:
\begin{itemize}
    \item \em{Spatial granularity}: the more specific the target of monitoring we can measure, the more efficient we can do optimization since we will know what causes the pitfalls of the energy consumption,
    \item \em{Temporal granularity}: same as spatial granularity, temporal granularity helps us to identify the sequence of code that need to be optimized,
    \item \em{Scalability}: this is mainly related to the cost of the tools and the ease of their integration into our system,
    \item  \em{Accuracy}: to eliminate extra hazards and get a more representative measurement.
\end{itemize}

We believe that accuracy can be extracted from these criteria by combining the first two results. Therefore, we will focus more on the first three criteria later on.
Below, we will discuss some of the well-known tools used in literature.

>>>>

% depends on the scientific usage there are two apporaches :
% 1. extern one or independent : when the most of researchs are using
% the benifits of this is the simplicity of instalation however we pay the price either with a lack of temporal resolution ( low frequency ) or the spatial granularity
% ( most of them measure the energy consumption of the whole machine )
% 2. dedicated one , they are based on the instrumentation of some parts of the computer , however they have a high cost and they are defficult to scale since they require an instrumentation of the execusion environment.
According to \citeauthor{hackenberg2014hdeem}, there are four main criteria to evaluate an energy measurement tool~\cite{hackenberg2014hdeem}:
\begin{itemize}
    \item \em{Spatial granularity}: the more specific the target of monitoring we can measure, the more efficient we can do optimization since we will know what causes the pitfalls of the energy consumption,
    \item \em{Temporal granularity}: same as spatial granularity, temporal granularity helps us to identify the sequence of code that need to be optimized,
    \item \em{Scalability}: this is mainly related to the cost of the tools and the ease of their integration into our system,
    \item  \em{Precision}: to eliminate extra hazards and get a more representative measurement.
\end{itemize}

We believe that precision can be extracted from these criteria by combining the first two results. Therefore, we will focus more on the first three criteria later on.
Below, we will discuss some of the well-known tools used in literature.
